Rigid fluid coupling

### 2022-05-11 manuscript/paper.tex
Add cylinder rolling benchmark.

>>>>

\FloatBarrier%
\subsection{Cylinder rolling on an inclined plane}
\label{sec:cylinder-rolling-on-an-inclined-plane}

\begin{figure}[!htpb]
  \centering
  \includegraphics[width=0.4\textwidth]{figures/de_2021_cylinder_rolling_on_an_inclined_plane_2d/fric_coeff_0_3/xcom_vs_time}
  \caption{x com vs time of a cylinder with a friction coefficient of $0.3$.}
\label{fig:cylinder-xcom-vs-time-fric-0-3}
\end{figure}

\begin{figure}[!htpb]
  \centering
  \includegraphics[width=0.4\textwidth]{figures/de_2021_cylinder_rolling_on_an_inclined_plane_2d/fric_coeff_0_6/xcom_vs_time}
  \caption{x com vs time of a cylinder with a friction coefficient of $0.6$.}
\label{fig:cylinder-xcom-vs-time-fric-0-6}
\end{figure}
